Impact of the 2016 Presidential Election on Urban Mobility: Who is Affected the Most?

### 2019-12-07 manuscript.Rmd

travel_time_sf <- travel_time_sf %>%
  mutate(distance = st_distance(centroids, mnm_sf$geometry, by_element = TRUE)) %>%
  mutate(march_inaug = 0)

travel_time_sf[11122:11676, "march_inaug"] = 1
#entries 11122 to 11676
```

@@

```{r}
st_queen <- function(a, b = a) st_relate(a, b, pattern = "F***T****")
as.nb.sgbp <- function(x, ...) {
  attrs <- attributes(x)
  x <- lapply(x, function(i) { if(length(i) == 0L) 0L else i } )
  attributes(x) <- attrs
  class(x) <- "nb"
  x
}

Queen <- as.nb.sgbp(st_queen(mod1data))
W <- nb2mat(Queen, style='B', zero.policy = TRUE)

@@

@@

>>>>

travel_time_sf <- travel_time_sf %>%
  mutate(distance = st_distance(centroids, mnm_sf$geometry, by_element = TRUE),
  			 march_inaug = ifelse((year == 2017 & month == 1 & week %in% c(3, 4)), 1, 0))
```

@@

```{r}
st_queen <- function(a, b = a) st_relate(a, b, pattern = "F***T****")
as.nb.sgbp <- function(x, ...) {
  attrs <- attributes(x)
  x <- lapply(x, function(i) { if(length(i) == 0L) 0L else i } )
  attributes(x) <- attrs
  class(x) <- "nb"
  x
}
```

```{r}
Queen <- as.nb.sgbp(st_queen(mod1data))
W <- nb2mat(Queen, style='B', zero.policy = TRUE)

@@

summary(dc_sar2)

Queen <- as.nb.sgbp(st_queen(weeks34))
W <- nb2mat(Queen, style='B', zero.policy = TRUE)

plot(weeks34["mean_travel_time"])
plot(Queen, weekw34$centroids, col="blue", cex = 0.5, lwd = 0.5)
```

@@

```{r}
Moran.I(week_1$mean_travel_time, W, na.rm=TRUE)
```

```{r travel_time_variance}
travel_time_sf_nontreat <- travel_time_sf %>%
	filter(march_inaug == 0) %>%
	group_by(GEOID) %>%
	summarise(mtt_mean = mean(mean_travel_time),
						mtt_var = var(mean_travel_time),
						mtt_sd = sd(mean_travel_time),
						NumRoads = log(mean(NumRoads) + 0.0001),
						NumMetro = log(mean(NumMetro + 0.0001)))
```

```{r}
travel_time_sf_nontreat %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mtt_mean)) +
	theme_map +
	scale_fill_viridis_c()

travel_time_sf_nontreat %>%
	ggplot() +
	geom_sf(mapping = aes(fill = mtt_sd)) +
	theme_map +
	scale_fill_viridis_c()

travel_time_sf_nontreat %>%
	ggplot() +
	geom_sf(mapping = aes(fill = NumRoads)) +
	theme_map +
	scale_fill_viridis_c()

travel_time_sf_nontreat %>%
	ggplot() +
	geom_sf(mapping = aes(fill = NumMetro)) +
	theme_map +
	scale_fill_viridis_c()
```
